---
title: "Assignment 1 (Trump Approval Ratings)"
Author: Brett D
output:
  html_document: default
  pdf_document: default
---
Overview: The data set that i selected is 'https://projects.fivethirtyeight.com/trump-approval-ratings/',
  the approval rating for president donald trump.  I wished to understand how his
  approval rates have trended over time, while attmeping to control for party affiliation.
```{r}
#Load the data from github into a data frame, create columns for percentage, and study length.

source = "https://raw.githubusercontent.com/fivethirtyeight/covid-19-polls/master/covid_approval_polls.csv"
data = read.csv(source)
df = data.frame(
  Start_Date = as.Date(data[,c("start_date")]),
  Poll_Length = as.Date(data[,c("end_date")]) - as.Date(data[,c("start_date")]),
  Party = data[,c("party")],
  Pollster  = data[,c('pollster')],
  Sample_Size  = data[,c("sample_size")],
  Approval_Percentage = (data[,c("approve")] / (data[,c("approve")] + data[,c("disapprove")])) * 100
)

```

```{r}
#visualize the data in ggplot
library(ggplot2)
ggplot(df) + geom_point(aes(x=Start_Date, y=Approval_Percentage, color=Party))
```



Findings: In conclusion, to the surprise of no one, republican view donald trump more favorable than democrats.  What I DID find interesting however, is that in early april, there was a spike in approval for the president among democrats that isn't shared by republicans.  Further research is needed to understand what might have happened during this time to cause this anomaly.
